Composable Algebra with Dependencies

### 2015-04-18 dAlg/mrm.tex
Wrap up

This paper presents composable algebra with dependencies: a new approach to compose 
algebras together to allow dependent interpretations with {\em fold}. 
For a given datatype represented by two-evel-types\cite{sheard04}, if one of its 
interpretations depends on a second interpretation, we compose the algebra correponding 
to this interpretation with the algebra corresponding to the second one, and use the 
composed algebra with {\em fold} to evaluate the expression.

@@

Apart from {\em two-level-types}, there are other ways to represent and evaluate
the DSL of parallel prefix circuits. In this section, we will show two other 
representations, and how they can be used to allow dependent interpretations.

>>>>

This paper presents composable algebra with dependencies: a new approach to compose 
algebras together to allow dependent interpretations with {\em fold}. 
For a given datatype represented by two-level-types\cite{sheard04}, if one of its 
interpretations depends on a second one, we compose the algebra correponding 
to the first interpretation with the one corresponding to the second, and use the 
composed algebra with {\em fold} to evaluate the expression. We present our approach 
on top of the domain specific language for parallel prefix circuits.

@@

Apart from {\em two-level-types}, there are other ways to represent and evaluate
the DSL for parallel prefix circuits. In this section, we will show two other 
representations, and how they can be used to allow dependent interpretations.
